---
title: "DRS 0000 Analysis: A Title of Some Sort"
author: "Jake Roden-Foreman"
date: "`r Sys.time()`"
output:
  html_document:
    pandoc_args: "--dpi=200"
    fig_height: 3
    fig_width: 5
    code_folding: show
    df_print: kable
    toc: true
    toc_depth: 1
    toc_float: true
knit: (function(inputFile, encoding) { 
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), "Write ups and reports", 'Analysis.html')) })
---

#### `r getwd()`
\
\


# Request Details {.tabset}

## Request Information  
ID:  
Status:   
Request Date:  
Required by date:  
Details:  
Purpose:  
Attachment:  
Previous Assignee:  
Decision making changes: 



## Requester Information  
Requester's Name:  
Requester's Capacity:  
Phone:  
Email:  
Address:  
Preferred Contact Method:  

# ---

\
\
\
\
\




# Analysis {.tabset}

## 1: Setup, Import, and Clean 
```{r}
knitr::opts_chunk$set(echo = TRUE, results = "asis")
options(kableExtra.auto_format = FALSE) #for proper table formating in Word
suppressMessages(library(tidyverse))
suppressMessages(library(tidylog))
suppressMessages(library(data.table))



```

\
\
\
\


## 2: Calculations
```{r}



```


\
\
\
\
\
\


# Results
```{r}



```






\
\
\
\
\
\
\
\
\

\
\
\
\
\
\



# ---

# Session Information
<style>
.footer {
  position: relative;
  left: 0;
  bottom: 0;
  width: 100%;
}
</style>

<div class="footer">

```{r}

pander::pander(sessionInfo())

```

</div>